Generative Adversarial Networks

### 2017-12-04 cs6735/project/report.tex
updated intro

\begin{abstract}
    Within the past decade, deep generative networks have often fallen short, especially when compared to deep discriminative models. However, since their inception in 2014, generative adversarial networks (GANs) have proved themselves as promising a research avenues for deep generative models. These networks now offer encouraging results for both unsupervised learning and generative models. The goal of this research paper is to present an overview of generative adversarial networks. Specifically, we will examine the motivation and challenges associated with GANs, their training process, architecture variations and some applications that are currently being explored.
\end{abstract}

>>>>

\begin{abstract}
    Within the past decade, deep generative networks have often fallen short, especially when compared to deep discriminative models. However, generative adversarial networks (GANs), first introduced in 2014 by Goodfollow \textit{et al.} \citep{2014arXiv1406.2661G}, have proved themselves as a promising research avenue for deep generative models. GANs present a new architecuture which allows for the unsupervised training of a generative model through backpropogation. Due to the current research effort, state-of-the-art results are now being acheived on a regular basis \citep{2017arXiv171010196K, 2017arXiv171111585W}; however, GANs still encounter instability during training and do not yet poccess the ability to produce completly realistic images. Nevertheless, these networks offer encouraging results for unsupervised learning, semi-supervised, reinforcement learning and several image generation tasks. This research paper will examine the motivations and challenges associated with GANs, their training process, architecture variations and some applications that are currently being explored.
\end{abstract}
